---
title: "Data605_HW1"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building the first letters for both first and last name using point plots:

First letters for the first name is "M" and the last name is "A"
The following code will build MA:

```{r }
x <- c(rep(-1,500),
       seq(-0.25,-1,length.out=500), 
       seq(-0.25,0.5,length.out=500), 
       rep(0.5,500),
       seq(1.25,2,length.out=500),
       seq(1.6,2.4,length.out=500),
       seq(2.75,2,length.out=500))
       
y <- c(seq(-2,1,length.out=500), 
       seq(-2,1,length.out=500), 
       seq(-2,1,length.out=500), 
       seq(-2,1,length.out=500),
       seq(-2,1,length.out=500),
       rep(-0.7,500),
       seq(-2,1,length.out=500))
       
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

```

# Writing R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix. Using a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3) rotation , and 4) projection in animated fashion.

```{r}
sq_mtx_mlt  <- function(x,y){
   x %*% y
}
```

# 1-Shearing
Shearing by taking the identity matrix and replacing one of the zero elements with a non-zero value:

```{r animation.hook="gifski"}

for (i in seq(0,1,length.out=20)) {
  z1<-apply(z,2,function(x) sq_mtx_mlt(x,matrix(c(1,i,0,1),nrow=2,ncol=2)))
   plot(z1[2,]~z1[1,], xlim=c(-3,3), ylim=c(-3,3))
}
```


# 2-Scaling
Scaling by multiplication of the values:

```{r animation.hook="gifski"}
for (i in seq(1,3,length.out=20)) {
  z1<-apply(z,2,function(x) sq_mtx_mlt(x,matrix(c(i,0,0,i),nrow=2,ncol=2)))
   plot(z1[2,]~z1[1,], xlim=c(-3,3), ylim=c(-3,3))
}

```


# 3-Rotation
Rotating counterclockwise through an angle 360 degrees with respect to the positive x axis about the origin of the two-dimensional system:

```{r animation.hook="gifski" }
for (i in seq(0,pi*2,length.out=20)) {
  z1<-apply(z,2,function(x) sq_mtx_mlt(x,matrix(c(cos(i),-sin(i),sin(i),cos(i)),nrow=2,ncol=2)))
   plot(z1[2,]~z1[1,], xlim=c(-3,3), ylim=c(-3,3))
}
```


# 4-Projection
Projection by rotating around the z-axis:

```{r animation.hook="gifski"}

for (i in seq(0,2*pi,length.out=20)) {
  zp<-rbind(z,rep(0,ncol(z)))
  z1<-apply(zp,2,function(x) sq_mtx_mlt(x,matrix(c(1,0,0,0,cos(i),-sin(i),0,sin(i),cos(i)),nrow=3,ncol=3)))
   plot(z1[2,]~z1[1,], xlim=c(-3,3), ylim=c(-3,3))
}

```


Reference: 
1.https://www.mathsisfun.com/algebra/matrix-transform.html
2.https://www.geeksforgeeks.org/computer-graphics-3d-rotation-transformations/amp/
3.https://bookdown.org/yihui/rmarkdown-cookbook/animation.html





